Temporal Split

### 2023-01-25 workflow/notebooks/temporal-split.Rmd

@@

calc_perf <- function(split) {
   get_performance_tbl(
        model,
        split$data,
        outcome_colname = 'idsa',
        perf_metric_function = caret::twoClassSummary,
        perf_metric_name = 'AUC',
        class_probs = TRUE,
        method = 'glmnet',
        seed = 100
      ) %>% 
    select(-c(method, seed)) %>% 
    pivot_longer(everything(), names_to = 'term', values_to = 'estimate')
}

@@

>>>>

```{r setup, include=FALSE}
schtools::set_knitr_opts()
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE,
                      fig.path = 'figures/')
```

@@

calc_perf <- function(split) {
   get_performance_tbl(
        model,
        analysis(split),
        outcome_colname = 'idsa',
        perf_metric_function = caret::multiClassSummary,
        perf_metric_name = 'AUC',
        class_probs = TRUE,
        method = 'glmnet',
        seed = 100
      ) %>% 
    select(-c(method, seed)) %>% 
    mutate(across(everything(), as.numeric)) %>% 
    pivot_longer(everything(), names_to = 'term', values_to = 'estimate')
}

@@

## Plot performance

```{r perf-95-ci}
perf_dat <- read_csv(here('results','temporal-split','performance_results.csv'))
perf_dat %>% 
  filter(term %in% c('cv_metric_AUC', "AUC")) %>% 
  mutate(term = case_when(term == 'cv_metric_AUC' ~ 'train AUROC',
                          term == 'AUC' ~ 'test AUROC',
                          TRUE ~ term)
  ) %>% 
  rename(estimate = .estimate,
         lower = .lower,
         upper = .upper) %>% 
  ggplot(aes(x = estimate, xmin = lower, xmax = upper, y = outcome, color = term)) +
  geom_pointrange(position = position_dodge(width = 0.1)) +
  schtools::theme_sovacool()
```
